Classless Java

### 2015-11-05 paper/sections/Formalization.tex
Typos on sect4
Typo2
comments on the formalization

@@

${}_{}$\\
\begin{figure}[h]
$
\!\!\!\!\!\!\!\!\!\!
\begin{array}{l}
\inferrule[(T-Invk)]{
\forall i\in 0..n  \Gamma \vdash \e_i \in \_<:\C_i \\\\
  \textsf{mtype}(\m,\C_0) \!=\! \C_1\ldots\C_n \!\!\to\! \C
%\textsf{mmodifier}(\m,\C_0) \neq \textbf{static} 
 }{
 \Gamma \vdash e_0.m(\overline{e}) \in \C }
\quad
\inferrule[(T-StaticInvk)]{
\forall i\in 1..n  \Gamma \vdash \e_i\in \_<:\C_i \\\\
\textsf{mtypeS}(\m,\C_0) \!=\! \C_1\ldots\C_n \!\!\to\! \C
%\textsf{mmodifier}(\m,\C_0) = \textbf{static} 
}{
\Gamma \vdash \C_0\QM.\m\QM(\e_1\ldots\e_n\QM) \in \C}
\quad
\inferrule[(T-SuperInvk)]{
\Gamma(\this) <: \C \\\\
\forall i\in 1..n  \Gamma \vdash \e_i\in \_<:\C_i \\\\
  \textsf{mtype}(\m,\C_0) \!=\! \C_1\ldots\C_n \!\!\to\! \C
%\textsf{mmodifier}(\m,\C_0) \neq \textbf{static} \\\\
}{\Gamma \vdash \C_0\QM.\QM{super}\QM.\m\QM(\e_1\ldots\e_n\QM) \in \C}

\\[5ex]
\inferrule[(T-Obj)]{
\forall i\in 1..n\ 
%\Gamma_i
\Gamma,\f_1{:}\T_1,\ldots,\f_k{:}\T_k,\,\QM{this}{:}\C,\Gamma^{\mh_i}
\vdash\e_i\in \_\subtype\C^{\mh_i}\\\\
\forall i\in 1..n\ \mh_i\subtype\mBody(\m^{\mh_i},\C)\\\\
\forall i\in 1..k\ \Gamma(\x)=\T_i\\\\
\forall\m\mbox{ such that }
\mBody(\m,\C)=\mh\QM; \exists i\in 1..n\ \m^{\mh_i}=\m
%\forall i\in 1\ldots n\ \Gamma_i=\Gamma,\f_1{:}\T_1,\ldots,\f_k{:}\T_k,\,\QM{this}{:}\C,\Gamma^{\mh_i}
}{
\Gamma \vdash\QM{new}\ \C\oR\cR\oC\T_1\ \f_1\QM=\x_1\QM;\ldots\T_k\ \f_k\QM=\x_k\QM;\
\mh_1\oC\QM{return}\ \e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_n\QM{;}\!\cC
\cC
\in\C
}
\quad
\inferrule[(T-Var)]{
\Gamma(\x)=\C
}{
\Gamma \vdash x \in\C}
\\[5ex]
 \inferrule[(T-Intf)]{
IT(\C_0) = \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \C_1\ldots\C_n \oC\methods\cC\\\\
 \forall \QM{default}\ \mh\oC\QM{return}\ \e\QM;\cC \in \methods,
\ \Gamma^{\mh},\,\QM{this}{:}\C\vdash\e\in \_\subtype\C^{\mh} \\\\
\dom(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(C_n)\cup\dom(\methods)
 }{
I \text{ OK}
}
\end{array}$
\caption{Typing}
\label{ET}
\end{figure}
\subsection{Grammar and typing rules}${}_{}$\\

@@

\override(\none,\method)=\method 
\whereNote
\mwhere\ \method\mbox{ not of the form } \conflicted\ \mh\QM;\\
\override(\method,\method')
=
\method 
\whereNote
\mwhere\ \method'\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}, \conflicted\ \mh\QM; \}\\
%\override(\method,\mh')
%=\method 
%\whereNote
%\mif\ \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \}, \mh\subtype\mh'
%\override(\_,\_)=\error & Otherwise
%\textsf{shadow}(body_1, body_2)=\emptyset & \textsf{if }body_1.\textsf{modifier}=body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\textsf{ or }body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_2 \hspace{.1in}  & \textsf{if }body_1=\emptyset\textsf{ or }body_1.\textsf{modifier}=\textbf{static}
\end{array}$

>>>>

\bruno{Some notes for discussion regarding formalization:
\begin{itemize}
\item Syntax and Rules: 
We can make it more compact and consistent by use overline 
notation more, instead of \ldots.
\item Order of premisses: It may be worthwhile to swap the order of 
some premisses, so that it follows the order of the explanations.
\item T-Invk: I think we need to type-check $e_0$ separately. Otherwise 
$C_0$ shows up magically.
\item T-Obj: small fixes on 3rd line. Suggestion, create two 
auxiliary functions: $sigvalid(C,\overline{mh})$ and $alldefined(C,\overline{mh})$
\item T-INTF: $C_0$ is $I$. Type of this was $C$, modified it to $C_0$.
In the last line, should it be $dom(\overline{meth})$ or just $\overline{meth}$?

\item tops and shadow: tops seems redundant; 
we use tops to collect classes, so just that in the next step we iterate 
over those classes to collect methods that satisfy some property. 
I think we can merge those 2 steps.

\item I have trouble following the definition of shadow; I think there 
are errors there.

\end{itemize}
}

@@

${}_{}$\\
\begin{figure}[h]
$
\!\!\!\!\!\!\!\!\!\!
\begin{array}{l}
\inferrule[(T-Invk)]{
\forall i\in 0..n\  \Gamma \vdash \e_i \in \_<:\C_i \\\\
  \textsf{mtype}(\m,\C_0) \!=\! \C_1\ldots\C_n \!\!\to\! \C
%\textsf{mmodifier}(\m,\C_0) \neq \textbf{static} 
 }{
 \Gamma \vdash \e_0\QM.\m\QM(\e_1\ldots\e_n\QM) \in \C }
\quad
\inferrule[(T-StaticInvk)]{
\forall i\in 1..n\  \Gamma \vdash \e_i\in \_<:\C_i \\\\
\textsf{mtypeS}(\m,\C_0) \!=\! \C_1\ldots\C_n \!\!\to\! \C
%\textsf{mmodifier}(\m,\C_0) = \textbf{static} 
}{
\Gamma \vdash \C_0\QM.\m\QM(\e_1\ldots\e_n\QM) \in \C}
\quad
\inferrule[(T-SuperInvk)]{
\Gamma(\this) <: \C_0 \\\\
\forall i\in 1..n\ \Gamma \vdash \e_i\in \_<:\C_i \\\\
  \textsf{mtype}(\m,\C_0) \!=\! \C_1\ldots\C_n \!\!\to\! \C
%\textsf{mmodifier}(\m,\C_0) \neq \textbf{static} \\\\
}{\Gamma \vdash \C_0\QM.\QM{super}\QM.\m\QM(\e_1\ldots\e_n\QM) \in \C}

\\[5ex]
\inferrule[(T-Obj)]{
\forall i\in 1..n\ 
%\Gamma_i
\Gamma,\f_1{:}\T_1,\ldots,\f_k{:}\T_k,\,\QM{this}{:}\C,\Gamma^{\mh_i}
\vdash\e_i\in \_\subtype\C^{\mh_i}\\\\
\forall i\in 1..n\ \mh_i\subtype\mBody(\m^{\mh_i},\C)\\\\
\forall i\in 1..k\ \Gamma(\x_i)\subtype\T_i\\\\
\forall\m\mbox{ such that }
\mBody(\m,\C)=\mh\QM; \exists i\in 1..n\ \m^{\mh_i}=\m
%\forall i\in 1\ldots n\ \Gamma_i=\Gamma,\f_1{:}\T_1,\ldots,\f_k{:}\T_k,\,\QM{this}{:}\C,\Gamma^{\mh_i}
}{
\Gamma \vdash\QM{new}\ \C\oR\cR\oC\T_1\ \f_1\QM=\x_1\QM;\ldots\T_k\ \f_k\QM=\x_k\QM;\
\mh_1\oC\QM{return}\ \e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_n\QM{;}\!\cC
\cC
\in\C
}
\quad
\inferrule[(T-Var)]{
\Gamma(\x)=\C
}{
\Gamma \vdash x \in\C}
\\[5ex]
 \inferrule[(T-Intf)]{
IT(\C_0) = \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \C_1\ldots\C_n \oC\methods\cC\\\\
 \forall \QM{default}\ \mh\oC\QM{return}\ \e\QM;\cC \in \methods,
\ \Gamma^{\mh},\,\QM{this}{:}\C_0\vdash\e\in \_\subtype\C^{\mh} \\\\
\dom(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(C_n)\cup\dom(\methods)
 }{
I \text{ OK}
}
\end{array}$
\caption{Typing}
\label{ET}
\end{figure}
\subsection{Grammar and typing rules}${}_{}$\\

@@

\override(\none,\method)=\method 
\whereNote
\mwhere\ \method\mbox{ not of the form } \conflicted\ \mh\QM;\\
\override(\method,\method')
=
\method 
\whereNote
\mwhere\ \method'\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@}, \conflicted\ \mh\QM; \},
\method\subtype\method'
\\
%\override(\method,\mh')
%=\method 
%\whereNote
%\mif\ \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \}, \mh\subtype\mh'
%\override(\_,\_)=\error & Otherwise
%\textsf{shadow}(body_1, body_2)=\emptyset & \textsf{if }body_1.\textsf{modifier}=body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_1 & \textsf{if }body_2=\emptyset\textsf{ or }body_2.\textsf{modifier}=\textbf{static}\\
%\textsf{shadow}(body_1, body_2)=body_2 \hspace{.1in}  & \textsf{if }body_1=\emptyset\textsf{ or }body_1.\textsf{modifier}=\textbf{static}
\end{array}$
